A comprehensive framework to capture the arcana of neuroimaging analysis

### 2018-10-17 manuscript/manuscript.tex
Tidied up arcana paper script
renamed nianalysis to banana

\begin{itemize}
\item The heterogeneous collection of neuroimaging analysis tools, parameters, styles makes it difficult to design comprehensive workflows
\item Complex workflows in a flexible extensible manner, reusable
\item portable between different data storage solutions/scale of studies, separation between design and application yet programmatic
\item Easily updatable, switchable between tools/versions
\end{itemize}

@@

The T1Study, T2starStudy and DmriStudy classes are
aggregated into a single MultiStudy class,
\emph{ArcanaPaper} (Supplementary material), which is specialised to produce
the figures in the Results section of this manuscript. In order to warp the
prior vein atlases to the subject space in the generation of the composite vein images,
nonlinear registration to Montreal Neurological Institute templates
\citep{mni-cite} is performed in the T1Study. The transform and warp
field from this registration are then mapped onto the `coreg\_to\_atlas\_mat` and
`coreg\_to\_atlas\_warp' specifications in the T2starStudy, instead
of registering the T2*-weighted images directly, in order to improve the registration.
These transforms were used to produce the composite vein
image in conjuction with the linear transform from the brain-extracted T2*-weighted
magnitude image to the brain extracted T1-weighted image, which required the
`brain' specification in the T1Study to be mapped to the `coreg\_ref\_brain`
specification in the T2starStudy.

@@

MR contrast-specific analyses are implemented in NiAnalysis via a chain
of successively specialised Study sub-classes (e.g.
MRI\textgreater{}EPI\textgreater{}dMRI) to enable generic processing
steps (e.g. registration) to be shared between classes. While not
necessary, it is recommended to create a subclass specific to the
research study in question and aggregate all related analysis within it,
since such classes can be applied to alternate datasets in order to
reproduce the exact analysis. The \emph{ArcanaPaper} class
(Supplementary material), which contains methods to generate all figures
in the Results section of this manuscript, is an example of this approach.

>>>>

\begin{itemize}
\item The heterogeneous collection of neuroimaging analysis tools, parameters, styles makes it difficult to design comprehensive workflows
\item Complex workflows in a flexible extensible manner, reusable
\item portable between different data storage solutions/scale of studies, separation between design and application yet programmatic, prototype locally and deploy on cluster
\item Easily updatable, switchable between tools/versions
\item Data specification, like make, dependencies are resolved by framework
\item Modular Repository, Processor, Environment and input matching
\item supports BIDS
\item provenance, checks for updates to find stale data and reprocesses
\item we have created a framework that handles all the tedious aspects and allows researchers to focus on the analysis design
\item it is flexible to allow researchers to collaborate
\end{itemize}

@@

The T1Study, T2starStudy and DmriStudy classes are
aggregated into a single MultiStudy class,
\emph{ArcanaPaper} (Supplementary material), which is specialised to produce
the figures in the Results section of this manuscript. In order to warp the
prior vein atlases to the subject space in the generation of the composite vein images,
nonlinear registration to Montreal Neurological Institute templates
\citep{grabner_symmetric_2006} is performed in the T1Study. The transform and warp
field from this registration are then mapped onto the `coreg\_to\_atlas\_mat` and
`coreg\_to\_atlas\_warp' specifications in the T2starStudy, instead
of registering the T2*-weighted images directly, in order to improve the registration.
These transforms were used to produce the composite vein
image in conjuction with the linear transform from the brain-extracted T2*-weighted
magnitude image to the brain extracted T1-weighted image, which required the
`brain' specification in the T1Study to be mapped to the `coreg\_ref\_brain`
specification in the T2starStudy.

@@

MR contrast-specific analyses are implemented in banana via a chain
of successively specialised Study sub-classes (e.g.
MRI\textgreater{}EPI\textgreater{}dMRI) to enable generic processing
steps (e.g. registration) to be shared between classes. While not
necessary, it is recommended to create a subclass specific to the
research study in question and aggregate all related analysis within it,
since such classes can be applied to alternate datasets in order to
reproduce the exact analysis. The \emph{ArcanaPaper} class
(Supplementary material), which contains methods to generate all figures
in the Results section of this manuscript, is an example of this approach.
